Metadata collation

### 2023-10-04 metadata/parametadata_control.Rmd
Adding pooled samp wIS to metadata

```{r}
if(!file.exists("metadata/raw_data/mzml_timestamps.csv")){
  mzml_timestamps <- grabMSdata(all_filedata$filepath, grab_what = "metadata") %>%
    pluck("metadata") %>%
    select(filename, timestamp)
  write_csv(mzml_timestamps, "metadata/raw_data/mzml_timestamps.csv")
}
mzml_timestamps <- read_csv("metadata/raw_data/mzml_timestamps.csv") %>%
  distinct()
parametadata <- all_filedata %>%
  left_join(mzml_timestamps, by="filename")
```

@@

```{r write out}
write_csv(parametadata, file = "metadata/parametadata.csv")
```

>>>>

```{r}
if(!file.exists("metadata/raw_data/mzml_timestamps.csv")){
  mzml_timestamps <- grabMSdata(all_filedata$filepath, grab_what = "metadata") %>%
    pluck("metadata") %>%
    select(filename, timestamp)
  write_csv(mzml_timestamps, "metadata/raw_data/mzml_timestamps.csv")
}
mzml_timestamps <- read_csv("metadata/raw_data/mzml_timestamps.csv") %>%
  distinct()
parametadata_all <- all_filedata %>%
  left_join(mzml_timestamps, by="filename")
```

@@

```{r write out}
write_csv(parametadata_all, file = "metadata/parametadata.csv")
```
